Spin canonical rings of log stacky curves

### 2015-07-03 stacky_write_up/spin_cring.tex
address many peter todos, "revert" main g0 thm pf

\todo{Make sure we call all divisors spin canonical divisors}
\todo{Write all block orders as tensors so we don't need to say the $y_i$ preceede the $x_i$.}
\todo{It's a bit strange how many tables are split across pages. Can we we make sure they each lie on a single page.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup of
$PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations. \todo{Peter: In the abstract we say finite area.  Don't we want that here as well?}  
We consider the graded {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$ \todo{Peter: Is $k$ bad to use here, since we will implicitly later use $k$ as the base field?}. One of the best
ways to understand the ring of modular forms is to give a
presentation as a quotient of a polynomial ring.
%of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
To do so, it is useful to have a bound on the
degrees in which the generators and relations can occur. In the
special case that $\Gamma$ has no odd weight modular forms, Voight
and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
 This paper \todo{Peter: I changed ``work to paper.'' Either way, it is a little awkward, because this could refer to VZB, or the one we are writing (of course I know it is the latter, but the reader won't)} extends their work to all Fuchsian groups $\Gamma$.

We can now consider the orbifold $\Gamma \backslash \BH$ over $\BC$.
For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
\backslash \BH$ is a Riemann Surface over $\BC$.  $\Gamma \backslash \BH$ may be non-compact, but in such cases we can form a
compact Riemann Surface, $\Gamma \backslash \BH^*,$ by adding in
cusps, with associated divisor of cusps $\Delta$.\todo{Peter: It is weird to have our first discussion of divisors be about the divisors of cusps.  Shouldn't canonical or half canonical divisors be introduced first?}

In order to find generators and relations for $M(\Gamma)$, we
translate the seemingly analytic question of understanding the ring
of modular forms into the algebraic category, using a
generalization of the GAGA principle: there is an equivalence of categories between orbifold
curves and log stacky curves over $\BC$ \cite[Proposition 6.1.5]
{vzb:stacky}. Hence, for the remainder
of the paper, we will work in the algebraic category.

@@

\noindent
with multiplication structure corresponding to tensor product of
sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
\cong \proj R$ \todo{Peter: I'm confused.  Why is this only true when $g\geq 2$?}. When $g \geq 2$, Petri's theorem gives generators
and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
is generated in degree 1 with relations in degree 2, as shown in
\cite[p. 157]{saint-donat:proj} and Arbarello--Cornalba--Griffiths--Harris
\cite[Section 3.3]{acgh:algebraic-curves}. This has the pleasant 
geometric consequence that all such canonically embedded curves are
scheme theoretically cut out by degree 2 equations.

@@

In particular, we bound the degrees of generators and relations of a
log spin canonical ring. Let
$\sx$ be a stacky curve with signature $\sigma = (g; e_1, \ldots,
e_r; \delta)$. The application of O'Dorney's work to log spin
canonical rings gives a weak bound in the case $g = 0$ in
terms of the least common multiples of the $e_i$'s \cite[Chapter 5]
{dorney:canonical}. In their treatment of log spin canonical
rings, Voight and Zureick-Brown bounded generator degrees by $3 \cdot \max(5, e_1, \ldots, e_r)$
and relation degrees by $3 \cdot \max(5, e_1, \ldots, e_r)$ when $\halfcan$ is effective
\cite[Corollary 10.4.6]{vzb:stacky}. \todo{Peter: Seems a bit misleading by misrepresenting VZB's work; in reality they found fairly tight bounds in the case they worked in.}

@@

\begin{rem}
\label{rem:main-weaker-assumptions}
In fact, the proof of Theorem ~\ref{thm:main} holds not only for log spin canonical divisors, which must have distinct points, but also for arbitrary effective divisors
$\Delta$. \todo{Peter: $\Delta$ seems weird as the name of the divisor, since its typically reserved for log divisors.  Also, how is this true?  This only follows given sufficient base point freeness conditions.  It is true when $g=0$ if that's what you meant to say.} Furthermore, one may relax the assumption that $k$ is perfect. Instead, one only need assume that the stacky curve
is separably rooted, i.e. the residue field at each stacky point
is separable.
\end{rem}
\todo{Peter: This remark seems to say two very separate things.  Why are they in the same remark?}

Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.  In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two we have to explicitly construct specific base cases and present a finite list of exceptional cases, while in the high genus case we deduce base cases from more general arguments.
\begin{rem}
\label{rem:explicit-generators}
The proofs of the main theorems in the low genus cases not only
obtain bounds on the degrees of the generators and relations, but
also yield explicit systems of generators and an explicit initial ideal of
relations. Furthermore, our proof of the high genus case also
provides an inductive procedure for explicitly determining the 
generators and initial ideal of relations of log spin canonical
rings. Many explicit systems of generators and relations are
detailed in interesting low genus examples by Neves
\cite[Section III.4]{neves:halfcan}.  \todo{Peter: The statement about the high genus case seems a bit unclear/misleading}

Furthermore, explicit constructions also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
Specifically, in almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
\end{rem}  \todo{Peter: Again, why are these two sections of the remark grouped together?}

%The main theorem of this paper, Theorem ~\ref{thm:main}, combined
%with a lemma of Voight and Zureick-Brown \cite[Lemma 10.2.1]
%{vzb:stacky}, provides a statement on all rings of modular forms.
Together with a theorem from Voight and Zureick-Brown \cite
[Theorem 9.3.1]{vzb:stacky} 
%and \cite[Theorem 9.3.1]{vzb:stacky}, 
\todo{Peter: The paragraph used to be confusingly redundant.  I think I fixed it but read through the commented out stuff to make sure it says the correct thing.}
we have the following application to
rings of modular forms. 
%Note that the lemma from Voight and Zureick-
%Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
%from the classical work of Kodaira--Spencer
%\cite{kodaira-spencer:deformations}.

@@

If $M_k(\Gamma) = 0$ for all odd $k$, then the ring of modular
forms $M(\Gamma)$ is generated as a $\BC$-algebra by elements of
degree at most $3 \cdot \max(3, e_1, \ldots, e_r)$ with relations
generated in degrees at most $6 \cdot \max(3, e_1, \ldots, e_r)$.\todo{Peter: Are you sure it shouldn't be $6e$ and $12e$, because he showed the {\emph canonical ring} has the bounds $3e$ and $6e$, which would mean the {\emph half-canonical} ring should have bounds $6e$ and $12e$ right?}

@@

In this paper, all stacky curves are assumed to be tame and
$k$ will is assumed to be algebraically closed. We also assume that the
stacky curves are separably rooted, i.e. the residue field of each
of the stacky points is separable.  \todo{Peter: We should clarify this last statement.  If we are assuming $k$ is algebraically closed, aren't the points automatically seperably-rooted?  Really aren't we saying if perfect, then restrict to algebraically closed, and if not, everything works similarly as long as separably rooted?}

@@

A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is
called a \textbf{log stacky curve} and the study of their
canonical rings is the main focus of the work by Voight and Zureick-
Brown \cite{vzb:stacky}. For this paper, we consider \textbf{log
spin curves} which are triples $(\sx, \Delta, \halfcan)$ where $\sx$
is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di
\sx$ satisfies $2 \halfcan \sim K_X + \Delta + \sum_{i = 1}^{r}
\frac{e_i - 1}{e_i} P_i$. Such a divisor $\halfcan$ is called a
\textbf{log spin canonical divisor} on $(\sx, \Delta)$. We use
$\halfcan_X := \lfloor L \rfloor $ to refer to the \textbf{spin
canonical divisor} (also known as the half-canonical divisor, semi-
canonical divisor, or theta characteristic) \todo{Peter: I think we mismatched the parenthetical.  Also, why did we define the spin canonical rdivisor of $\halfcan_X$ especially.  Isn't it really just a special case of the definition before.} associated to the
coarse space $X$ of $\sx$  (i.e. $\halfcan_X$ is a divisor such
that $2\halfcan_X \sim K_X + \Delta$). 
We define $H^0$ of a stacky divisor as follows:

@@

Now, we check the admissibility of $J= \{2, 3\}$ (corresponding to the $e_2,e_3=7$). By relabelling the
variables if necessary, we can assume that $x_{7, 1}$ corresponds
to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
correspond to the generator with maximal pole order at $P_3$. Use
the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
\ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{custom:Ad-ii} We may also choose
pole orders of the generators such that $y_{i, e_i'}$ is the only
generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
generators lying below the line as seen in Figure ~\ref{fig:377}
(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
$x_{7, 2}$ respectively).

@@

\begin{align*}
	\dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / I\right)_d &=
	\dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ \initial(I)\right)_d \\
	&= \dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle
	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_d
\end{align*}\todo{Peter: I think you need additional degree subscripts added to the polynomial ring or something, so this isn't infinite.}

@@

First, if $P$ is not a basepoint of $\halfcan',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
\iffalse
In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor \halfcan|_P \rfloor $,
as $P$ is not a basepoint of $L_X'$. Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg \halfcan' \geq 1.$   \todo{Peter: I don't find this paragraph (after the first sentence) very useful.  1: I'm not sure if we even need to go through the check that it satisfies the conditions for lemma 4.5.  2: I don't find the check clear or illuminating as written.  Either we should reword it or remove it (feel free to disagree, of course)}
\fi
Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $\halfcan= \halfcan'+P$.

@@

\vskip.1in
\noindent
{\sf Case 2b: $L_X = 0$}

@@

\todo{Peter: Maybe you should mention something about how the exceptional cases differ, and how this affects the argument? Ok, I did it imprecisely. Is this better?}
\end{proof}

@@

	\caption{Genus 0 Non-effective Base Cases Generators/Relations}
	\label{table:g-0-base-cases-degrees}
\end{longtable}
\todo{Peter: Can we make a better description for the table above?}

@@

	\caption{Genus 0 Non-Effective Base Cases \ref{custom:Ad-iii}}
	\label{table:g-0-base-cases-admissibility}
\end{longtable}
\todo{Peter: In case c, I changed $J=\{3\}$ to $J=\{2, 3\}$.}
\todo{Peter: I don't particularly like split tables.  Might we consider not using [h], so its not split}

@@

Now we can use Lemma ~\ref{lem:sat-3}, Lemma
~\ref{lem:raise-stacky-order}, and Corollary
~\ref{cor:raise-stacky-order} to induct from the cases of Table
~\ref{table:g-0-base-cases} and obtain the desired bounds on the
generator and relation degrees for log spin canonical rings of
genus 0 curves. This process will be carried out in Subsection
~\ref{ssec:g-0-main}.
\todo{Peter: I don't think this paragraph should be here.  It seems like its kind of redundant given section 7.4.  Maybe, we could just, say something like ``these provide the base cases, from which we will induct in section 7.4.''}
%Through the application of two inductively adding 
%points via Lemma ~\ref{lem:sat-3} and inductively raising
%stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
%we obtain Theorem ~\ref{thm:g-0-main} for any
%log spin curve $(\sx, \Delta, L)$ with
%signature $\sigma$ covered by this induction process.
%In particular, this induction process covers all signatures $\sigma
%= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
%for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
%\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
%Before we prove the main theorem, we describe the cases not be
%covered by induction.

@@

	$(0; 3, 3, 3; 0)$ & $\{3\}$ & $\emptyset$ & $3$ \\	\hline

@@

	$(0; 3, 3, 3, 3; 0)$ & $\{3, 3, 4\}$ & $\{12\}$ & $3$ \\	\hline

	\caption{Genus 0 Exceptional Cases}
	\label{table:g-0-exceptional}
\end{longtable}
\todo{Peter: Technically, shouldn't the first and last $e$ be 5 instead of 3, since $e=\max(5, e_i)$?}

\begin{rem}
These cases give all of the exceptions to the $e$ and $2e$ bounds on
the generator and relation degree. Notice that each of these
exceptional cases, apart from $(0; 3, 5, 7; 0)$, has saturation not in $\{3, 5, 9\}$ as seen in Table ~\ref{table:g-0-sat}.
Heuristically, \todo{Peter: Is heuristically the right word here?  I interpret heuristically to mean ``providing a technique or method to solve a problem,'' whereas I think you mean something more along the lines of intuitively.}
these exceptional saturations can be viewed as ``forcing'' generators and relations in higher degrees than expected.
\end{rem}

@@

\begin{proof}
If $\sx$ has no stacky points, then we can assume that $L \sim
n \cdot \infty$ with $n \in \BZ$.  When $n=-1$, then $R_\halfcan=k$.  When $n=0$, then $R_\halfcan = k[x]$.  When $n>0$, inductively applying Lemma \ref{lem:sat-1} tells us that $R_\halfcan$ is generated in degree 1 with relations generated in degree 2.  All three of these cases meet the conclusion of Theorem \ref{thm:g-0-main}.

First, consider the case when $\delta \geq 2$. \todo{Peter: it feels a tiny bit redundant here, as we kind of said this in the introduction to the section.}
 In any such cases,
$\halfcan_X$ is an effective divisor so we can inductively apply
the Lemma ~\ref{lem:sat-1} from the classical non-stacky case
to deduce that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
with relations generated up to degree $2e$.

By Remark ~\ref{rem:delta-not-1}, it only remains to deal with the case $\delta = 0$, so $\halfcan_X$ is not effective.
Let $\sigma = (0; e_1, \ldots, e_r; 0)$ not be one of the exceptional cases in Table
~\ref{table:g-0-exceptional}.  We get the following three cases, depending on the value of $r$:

\vskip.1in
\noindent
{\sf Case 1: $r<3$}

If $r < 3$, then $\deg 
\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we get the
trivial ring $R(\sx, \Delta, \halfcan) = k$.

\vskip.1in
\noindent
{\sf Case 2: $3\le r \le 5$}

If $3\le r \leq 5$ and $\sigma$ is not one of the exceptional cases,
then we may apply Lemma ~\ref{lem:g-0-admissible-cases} and
Corollary ~\ref{cor:raise-stacky-order} to an appropriate base case
from Table ~\ref{table:g-0-base-cases} and deduce that $R(\sx,
\delta, \halfcan)$ is generated up  to degree $e := \max(5, e_1,
\ldots, e_r)$ with relations generated up to degree $2e$.

>>>>

\todo{Make sure we call all divisors spin canonical divisors}
\todo{Make sure we want to have linear equivalence $\sim$ of divisors instead of $=$ in most places}
\todo{Write all block orders as tensors so we don't need to say the $y_i$ precede the $x_i$.}
\todo{It's a bit strange how many tables are split across pages. Can we we make sure they each lie on a single page. Robin: do this at the end, not yet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup of
$PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations. \todo{Peter: In the abstract we say finite area.  Don't we want that here as well?}  
We consider the graded {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$ \todo{Peter: Is $k$ bad to use here, since we will implicitly later use $k$ as the base field? Robin: Perhaps, although modular forms are traditionally referred to as having weight $k$. Not sure on this one.}. One of the best
ways to understand the ring of modular forms is to give a
presentation as a quotient of a polynomial ring.
%of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
To do so, it is useful to have a bound on the
degrees in which the generators and relations can occur. In the
special case that $\Gamma$ has no odd weight modular forms, Voight
and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
We extend their result to all Fuchsian groups $\Gamma$ in the main
theorem of this work.

We can now consider the orbifold $\Gamma \backslash \BH$ over $\BC$.
For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
\backslash \BH$ is a Riemann Surface over $\BC$. 
$\Gamma \backslash \BH$ may be non-compact, but in such cases we can form a
compact Riemann Surface, $\Gamma \backslash \BH^*,$ by adding in
cusps, with associated divisor of cusps $\Delta$.\todo{Peter: It is weird to have our first discussion of divisors be about the divisors of cusps.  Shouldn't canonical or half canonical divisors be introduced first? Robin: But this is where the log divisor comes from!}

In order to find generators and relations for $M(\Gamma)$, we
translate the seemingly analytic question of understanding the ring
of modular forms into the algebraic category, using a
generalization of the GAGA principle. By \cite[Proposition 6.1.5]
{vzb:stacky}, there is an equivalence of categories between orbifold
curves and log stacky curves over $\BC$. Hence, for the remainder
of the paper, we will work in the algebraic category.
\todo{Robin: I changed this back because the new version seemed a bit
long and the period is perfectly acceptable here. the new version
seemed oddly worded to me}

@@

\noindent
with multiplication structure corresponding to tensor product of
sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
\cong \proj R$ \todo{Peter: I'm confused.  Why is this only true when $g\geq 2$? Robin: see statement of Petri's theorem...}. When $g \geq 2$, Petri's theorem gives generators
and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
is generated in degree 1 with relations in degree 2, as shown in
\cite[p. 157]{saint-donat:proj} and Arbarello--Cornalba--Griffiths--Harris
\cite[Section 3.3]{acgh:algebraic-curves}. This has the pleasant 
geometric consequence that all such canonically embedded curves are
scheme theoretically cut out by degree 2 equations.

@@

In particular, we bound the degrees of generators and relations of a
log spin canonical ring. Let
$\sx$ be a stacky curve with signature $\sigma = (g; e_1, \ldots,
e_r; \delta)$. The application of O'Dorney's work to log spin
canonical rings gives a weak bound in the case $g = 0$ in
terms of the least common multiples of the $e_i$'s \cite[Chapter 5]
{dorney:canonical}. In their treatment of log spin canonical
rings, Voight and Zureick-Brown bounded generator degrees by $3 \cdot \max(5, e_1, \ldots, e_r)$
and relation degrees by $3 \cdot \max(5, e_1, \ldots, e_r)$ when $\halfcan$ is effective
\cite[Corollary 10.4.6]{vzb:stacky}. \todo{Peter: Seems a bit misleading by misrepresenting VZB's work; in reality they found fairly tight bounds in the case they worked in. Robin: How? This solely talks about their work for the log spin canonical rings which is clearly NOT tight. They give a larger bound than us for a subset of the cases we check...}

@@

\begin{rem}
\label{rem:main-weaker-assumptions}
In fact, the proof of Theorem ~\ref{thm:main} holds not only for log spin canonical divisors, which must have distinct points, but also for arbitrary effective divisors
$\Delta$. \todo{Peter: $\Delta$ seems weird as the name of the divisor, since its typically reserved for log divisors.  Also, how is this true?  This only follows given sufficient base point freeness conditions.  It is true when $g=0$ if that's what you meant to say. Robin: Throughout VZB, for example, $\Delta$ is used to represent any effective divisor. Where does an assumption that $\Delta$ has coefficient $1$ come into play?} Furthermore, one may relax the assumption that $k$ is perfect. Instead, one only need assume that the stacky curve
is separably rooted, i.e. the residue field at each stacky point
is separable.
\end{rem}
\todo{Peter: This remark seems to say two very separate things.  Why are they in the same remark? Robin: This remark describes how the weaker conditions for which the theorem also holds.}

Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.  In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two we have to explicitly construct specific base cases and present a finite list of exceptional cases, while in the high genus case we deduce base cases from more general arguments.
\begin{rem}
\label{rem:explicit-generators}
The proofs of the main theorems in the low genus cases not only
obtain bounds on the degrees of the generators and relations, but
also yield explicit systems of generators and an explicit initial ideal of
relations. Furthermore, our proof of the high genus case also
provides an inductive procedure for explicitly determining the 
generators and initial ideal of relations of log spin canonical
rings. Many explicit systems of generators and relations are
detailed in interesting low genus examples by Neves
\cite[Section III.4]{neves:halfcan}.  \todo{Peter: The statement about the high genus case seems a bit unclear/misleading Robin: how so}

Furthermore, explicit constructions also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
Specifically, in almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
\end{rem}  \todo{Peter: Again, why are these two sections of the remark grouped together? Robin:Isn't this remark describing whether the theorem gives explicit constructions and tight bounds? Those seem pretty related...}

%The main theorem of this paper, Theorem ~\ref{thm:main}, combined
%with a lemma of Voight and Zureick-Brown \cite[Lemma 10.2.1]
%{vzb:stacky}, provides a statement on all rings of modular forms.
Together with a theorem from Voight and Zureick-Brown \cite
[Theorem 9.3.1]{vzb:stacky} 
%and \cite[Theorem 9.3.1]{vzb:stacky}, 
\todo{Peter: The paragraph used to be confusingly redundant.  I think I fixed it but read through the commented out stuff to make sure it says the correct thing. Robin: Why are you ignoring Lemma 10.2.1 as well as its connection to Kodaira--Spencer?}
we have the following application to
rings of modular forms. 
%Note that the lemma from Voight and Zureick-
%Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
%from the classical work of Kodaira--Spencer
%\cite{kodaira-spencer:deformations}.

@@

If $M_k(\Gamma) = 0$ for all odd $k$, then the ring of modular
forms $M(\Gamma)$ is generated as a $\BC$-algebra by elements of
degree at most $3 \cdot \max(3, e_1, \ldots, e_r)$ with relations
generated in degrees at most $6 \cdot \max(3, e_1, \ldots, e_r)$.\todo{Peter: Are you sure it shouldn't be $6e$ and $12e$, because he showed the {\emph canonical ring} has the bounds $3e$ and $6e$, which would mean the {\emph half-canonical} ring should have bounds $6e$ and $12e$ right? Robin: I think you are correct, although don't use $e$ since it is max(3, ...) instead of max(5, ...)}

@@

In this paper, all stacky curves are assumed to be tame and
$k$ will is assumed to be algebraically closed. We also assume that the
stacky curves are separably rooted, i.e. the residue field of each
of the stacky points is separable.  \todo{Peter: We should clarify this last statement.  If we are assuming $k$ is algebraically closed, aren't the points automatically separably-rooted?  Really aren't we saying if perfect, then restrict to algebraically closed, and if not, everything works similarly as long as separably rooted? Robin: Yes I guess $k$ being algebraically closed implies perfectness... we can use a similar statement to Remark 5.5.7 from VZB}

@@

A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is
called a \textbf{log stacky curve} and the study of their
canonical rings is the main focus of the work by Voight and Zureick-
Brown \cite{vzb:stacky}. For this paper, we consider \textbf{log
spin curves} which are triples $(\sx, \Delta, \halfcan)$ where $\sx$
is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di
\sx$ satisfies $2 \halfcan \sim K_X + \Delta + \sum_{i = 1}^{r}
\frac{e_i - 1}{e_i} P_i$. Such a divisor $\halfcan$ is called a
\textbf{log spin canonical divisor} on $(\sx, \Delta)$. We use
$\halfcan_X := \lfloor L \rfloor $ to refer to the \textbf{spin
canonical divisor} (also known as the half-canonical divisor, semi-
canonical divisor, or theta characteristic) \todo{Peter: I think we mismatched the parenthetical.  Also, why did we define the spin canonical divisor of $\halfcan_X$ especially.  Isn't it really just a special case of the definition before. Robin: How? the parenthetical encompasses all alternate names! Yes it's a special case, but we never give it a name otherwise. You could define it as the log spin canonical divisor with zero log divisor but that somehow doesn't seem to give the right picture.} associated to the
coarse space $X$ of $\sx$  (i.e. $\halfcan_X$ is a divisor such
that $2\halfcan_X \sim K_X + \Delta$). 
We define $H^0$ of a stacky divisor as follows:

@@

Now, we check the admissibility of $J= \{2, 3\}$ (corresponding to the $e_2,e_3=7$). \todo{Robin: I don't understand your edit, Peter. Admissibility is not a property of $J$.} By relabelling the
variables if necessary, we can assume that $x_{7, 1}$ corresponds
to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
correspond to the generator with maximal pole order at $P_3$. Use
the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
\ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{custom:Ad-ii} We may also choose
pole orders of the generators such that $y_{i, e_i'}$ is the only
generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
generators lying below the line as seen in Figure ~\ref{fig:377}
(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
$x_{7, 2}$ respectively).

@@

\begin{align*}
	\dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / I\right)_d &=
	\dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ \initial(I)\right)_d \\
	&= \dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle
	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_d
\end{align*}\todo{Peter: I think you need additional degree subscripts added to the polynomial ring or something, so this isn't infinite. Robin: Aren't there already existing degree subscripts?}

@@

First, if $P$ is not a basepoint of $\halfcan',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.

%In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor \halfcan|_P \rfloor $,
%as $P$ is not a basepoint of $L_X'$. Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg \halfcan' \geq 1.$   \todo{Peter: I don't find this paragraph (after the first sentence) very useful.  1: I'm not sure if we even need to go through the check that it satisfies the conditions for lemma 4.5.  2: I don't find the check clear or illuminating as written.  Either we should reword it or remove it (feel free to disagree, of course)}

Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $\halfcan= \halfcan'+P$.

@@

\vskip.1in
\noindent
{\sf Case 2b: $\halfcan_X = 0$}

@@

\todo{Peter: Maybe you should mention something about how the exceptional cases differ, and how this affects the argument? Aaron: Ok, I did it imprecisely. Is this better?}
\end{proof}

@@

	\caption{Genus 0 Non-effective Base Cases Generators/Relations}
	\label{table:g-0-base-cases-degrees}
\end{longtable}
\todo{Peter: Can we make a better description for the table above? Robin: Think of one.}

@@

	\caption{Genus 0 Non-Effective Base Cases \ref{custom:Ad-iii}}
	\label{table:g-0-base-cases-admissibility}
\end{longtable}

@@

%Now we can use Lemma ~\ref{lem:sat-3}, Lemma
%~\ref{lem:raise-stacky-order}, and Corollary
%~\ref{cor:raise-stacky-order} to induct from the cases of Table
%~\ref{table:g-0-base-cases} and obtain the desired bounds on the
%generator and relation degrees for log spin canonical rings of
%genus 0 curves. This process will be carried out in Subsection
%~\ref{ssec:g-0-main}.
%\todo{Peter: I don't think this paragraph should be here.  It seems like its kind of redundant given section 7.4.  Maybe, we could just, say something like ``these provide the base cases, from which we will induct in section 7.4.''}

%Through the application of two inductively adding 
%points via Lemma ~\ref{lem:sat-3} and inductively raising
%stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
%we obtain Theorem ~\ref{thm:g-0-main} for any
%log spin curve $(\sx, \Delta, L)$ with
%signature $\sigma$ covered by this induction process.
%In particular, this induction process covers all signatures $\sigma
%= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
%for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
%\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
%Before we prove the main theorem, we describe the cases not be
%covered by induction.

@@

	$(0; 3, 3, 3; 0)$ & $\{3\}$ & $\emptyset$ & $5$ \\	\hline

@@

	$(0; 3, 3, 3, 3; 0)$ & $\{3, 3, 4\}$ & $\{12\}$ & $5$ \\	\hline

	\caption{Genus 0 Exceptional Cases}
	\label{table:g-0-exceptional}
\end{longtable}

\begin{rem}
These cases give all of the exceptions to the $e$ and $2e$ bounds
on the generator and relation degree. Notice that each of these
exceptional cases, apart from $(0; 3, 5, 7; 0)$, also has
exceptional saturation as seen in Table ~\ref{table:g-0-sat}.
Intuitively, these exceptional saturations can be viewed as ``
forcing'' generators and relations in higher degrees than expected.
\end{rem}

@@

\begin{proof}
If $\sx$ has no stacky points, then we can assume that $L \sim
n \cdot \infty$ with $n \in \BZ_{\geq -1}$. This is a classical
case which is done by Voight and Zureick-Brown \cite[Section 4.2]
{vzb:stacky}. When $n = -1$, then $R_\halfcan = k$.  When $n = 0$,
then $R_\halfcan = k[x]$.  When $n > 0$, inductively applying Lemma
\ref{lem:sat-1} tells us that $R_\halfcan$ is generated in degree 1
with relations generated in degree 2.

First, let us consider the case when $\delta \geq 2$. In any such
case, $\lfloor \halfcan \rfloor$ is an effective divisor and the
conditions of Lemma ~\ref{lem:sat-1} are satisfied. Thus, we can
apply the Lemma ~\ref{lem:sat-1} inductively from the classical
case with no stacky points to get that $R(\sx, \Delta, \halfcan)$
is generated up to degree $e$.

By Remark ~\ref{rem:delta-not-1}, it only remains to deal with the
case $\delta = 0$, so $\halfcan$ is not necessarily effective. Let
the signature $\sigma$ be such that it is not one of the
exceptional cases contained in Table ~\ref{table:g-0-exceptional}. 
We get the following three cases, depending on the value of $r$:

\vskip.1in
\noindent
{\sf Case 1: $r < 3$}

If $r < 3$, then $\deg 
\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we have the
trivial case where $R(\sx, \Delta, \halfcan) = k$.

\vskip.1in
\noindent
{\sf Case 2: $3 \le r \le 5$}

If $3 \le r \leq 5$ and $\sigma$ is not one of the exceptional cases,
then we may apply Lemma ~\ref{lem:g-0-admissible-cases} and
Corollary ~\ref{cor:raise-stacky-order} to an appropriate base case
from Table ~\ref{table:g-0-base-cases} and deduce that $R(\sx,
\delta, \halfcan)$ is generated up  to degree $e := \max(5, e_1,
\ldots, e_r)$ with relations generated up to degree $2e$.
